Think deep for reef resilience

### 2025-08-16 paper/paper_draft.qmd
Address minor comment

The time series clustering was applied over the time frame between 2025 and 2075. Spatially,
the analyses were conducted for each GBR management area and at the scale of each reefal
bioregion (defined in GBRMPA [-@GBRMPA2024]). Analyses were also performed at the
whole-of-GBR scale but were found to lead to identical results **\[TI: Ben, compared to
what, the bioregion or the Management area results?\]** and so are not shown here. To
compare time series clustering results across GCMs, Management area scale clustering results
are used to preserve coarse scale latitudinal differences between regions, while maintaining
ease of comparison and visualisation. These comparisons include quantification of
differences between low and high cover clusters across management regions under each GCM
using the CID between cluster median time series. To assess how different reef
characteristics influence time series clustering at a finer spatial scale, bioregion results
are used to capture patterns occurring within individual clusters of reefs. Results of all
analyses at all clustering scales can be found at Grier and Iwanaga [-@grier2025] for those
interested.

>>>>

The time series clustering was applied over the time frame between 2025 and 2075. Spatially,
the analyses were conducted for each GBR management area and at the scale of each reefal
bioregion (defined in GBRMPA [-@GBRMPA2024]). Analyses were also performed at the
whole-of-GBR scale but were found to lead to identical conclusions about characteristics influencing cluster cover compared to management area and bioregion scale analyses, and so are not shown here. To
compare time series clustering results across GCMs, Management area scale clustering results
are used to preserve coarse scale latitudinal differences between regions, while maintaining
ease of comparison and visualisation. These comparisons include quantification of
differences between low and high cover clusters across management regions under each GCM
using the CID between cluster median time series. To assess how different reef
characteristics influence time series clustering at a finer spatial scale, bioregion results
are used to capture patterns occurring within individual clusters of reefs. Results of all
analyses at all clustering scales can be found at Grier and Iwanaga [-@grier2025] for those
interested.
